\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-25 trunk/arch.tex
updates to review

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:

>>>>

Traditionally planning has been deemed computationally expensive with
planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\kcomment{(\ie as it works to complete a goal)}if
the internal state of the plan gets out of synch with the actual state
of the world. As a result the planning problem managed {\em in situ}
has traditionally remained fairly detached from low-level
control. Most adaptations at the lower-level reactive layers in
contrast are managed by specialized components (for example
\texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner. The \rx architecture contributes to agent
architectures over and beyond \texttt{IDEA} in the following
\kcomment{significant} ways:

### 2012-04-25 trunk/europa.tex
updates to reviews
updates to review

@@

\begin{figure}[b]
\centering
\includegraphics[scale=0.4]{figs/EUROPA-Architecture.pdf}
\caption{\small The \eu software architecture.}
\label{fig:europa-architecture}
\end{figure}

@@

\item \textit{Temporal Network}: Extensions to the \texttt{CRE} module to
  reason about temporal constraints

@@

Since \eu supports a flexible temporal representation, where time is
represented by intervals, instead of single values, determining
whether a resource is the source of a plan flaw or a constraint
violation in general is substantially more difficult than just
computing a profile of the resource and checking against some limits.
With temporal flexibility, a number of resource profiles could be
possible depending on precisely when each production/consumption event
occurs out of a range of possible values that are in the domain of the
variables that represent the temporal extent for the event.
\cite{Muscettola04,Muscettola06} proposed an algorithm where the
variables that represent the time for production/consumption events
are placed in a temporal network, similar to the network used by the
temporal propagator; constraints on the resource can then be seen as
quantities flowing through that network. Computing the maximum flow
then, yields the maximum resource usage and thus a lower bound on the
resource level; computing a minimum flow will similarly yield an upper
bound. Since maximum flow on a temporal network can be computed in
polynomial time, \eu takes advantage of this algorithm to efficiently
compute upper and lower bound envelopes on the resource
level. Fig. \ref{fig:resenvelopes} shows an example of such a resource
computation.

\begin{figure}
\centering
\includegraphics[scale=0.2]{figs/europa-resource-envelopes.png}
\caption{\small An example of resource envelopes computed by \eu.}
\label{fig:resenvelopes}
\end{figure}

>>>>

\comment{I think we should expand on this section which, as the
  reviewer notes, the inter-relationships between the elements in Fig
  \ref{fig:europa-architecture} below is not fully captured. I think
  an illustrative example of how these components work together might
  be very useful. This might also help the sub-section end less
  abruptly than it is currently.}

@@

\begin{figure}[b]
\centering
\includegraphics[scale=0.5]{figs/EUROPA-Architecture.pdf}
\caption{\small The \eu software architecture.\comment{Is there a
    better block diagram we can use to respond to review comment on
    page 2?}}
\label{fig:europa-architecture}
\end{figure}

@@

\item \textit{Temporal Network}: Extensions to the \texttt{CRE} module to
  reason about temporal constraints.

@@

Since \eu supports a flexible temporal representation, where time is
represented by intervals, instead of single values, determining
whether a resource is the source of a plan flaw or a constraint
violation in general is substantially more difficult than just
computing a profile of the resource and checking against some limits.
With temporal flexibility, a number of resource profiles could be
possible depending on precisely when each production/consumption event
occurs out of a range of possible values that are in the domain of the
variables that represent the temporal extent for the event.
\cite{Muscettola04,Muscettola06} proposed an algorithm where the
variables that represent the time for production/consumption events
are placed in a temporal network, similar to the network used by the
temporal propagator; constraints on the resource can then be seen as
quantities flowing through that network. Computing the maximum flow
then, yields the maximum resource usage and thus a lower bound on the
resource level; computing a minimum flow will similarly yield an upper
bound. Since maximum flow on a temporal network can be computed in
polynomial time \comment{definition needed?}, \eu takes advantage of
this algorithm to efficiently compute upper and lower bound envelopes
on the resource level. Fig. \ref{fig:resenvelopes} shows an example of
such a resource computation.

\begin{figure}
\centering
\includegraphics[scale=0.3]{figs/europa-resource-envelopes.png}
\caption{\small An example of resource envelopes computed by \eu.}
\label{fig:resenvelopes}
\end{figure}
